Finite-state morphological transducers for three Kypchak languages

### 2013-10-24 kipchak-lrec-2013/kipchak-paper.tex
integrate map
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48175 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{booktabs}

@@

These languages belong to the Northwestern branch of Turkic, which is often referred to as the Kypchak branch.  This branch can be divided into three subbranches.  Kumyk is a member of the Western Kypchak group, Tatar is a member of the Northern Kypchak group, and Kazakh is a member of the Southern Kypchak group \citep[82-83]{histofturkic}.  As such, each of these three languages represents a different one of the three branches of Kypchak.  The geographic distribution of the languages is shown in map \ref{}.

@@

%FIXME: keep revision number up to date
The transducers are available / under development at \url{https://svn.code.sf.net/p/apertium/svn/languages/}, in the directories apertium-kaz, apertium-tat, and apertium-kum.  The revision of the entire subversion repository that the numbers (stem counts, evaluation, etc.) in this paper represent is \texttt{r48137}.

%FIXME: update for the three languages
The tagset consists of 127 separate tags, 19 covering the main parts of speech (noun, verb, adjective, adverb, postposition, etc.) and 108 covering morphological subcategorisation for e.g. case, number, person, possession, transitivity, tense-aspect-mood, etc. The tags are represented as multicharacter symbols, between less than `<' and greater than `>' symbols. The tagset is quite extensive and still not entirely stabilised, as such a full listing is not included here. However, the tags are listed in the source code of the transducer,\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/branches/apertium-kir/} testing} along with comments describing their usage.

>>>>

\usepackage{booktabs}
\usepackage{jnwmaps}

@@

These languages belong to the Northwestern branch of Turkic, which is often referred to as the Kypchak branch.  This branch can be divided into three subbranches.  Kumyk is a member of the Western Kypchak group, Tatar is a member of the Northern Kypchak group, and Kazakh is a member of the Southern Kypchak group \citep[82-83]{histofturkic}.  As such, each of these three languages represents a different one of the three branches of Kypchak.  The geographic distribution of the languages is shown in map \ref{map}.

\begin{map*}
	\label{map}
	\includegraphics[width=\textwidth]{map/map}
	\caption{The three branches of Kypchak (N, S, W), showing the distribution of the three languages for which transducers were developed (tat, kaz, kum).  Language codes are from ISO 639-3.}
\end{map*}

@@

%FIXME: keep revision number up to date
The transducers are available / under development in apertium's subversion repository,\footnote{\url{https://svn.code.sf.net/p/apertium/svn/languages/}} in the directories apertium-kaz, apertium-tat, and apertium-kum.  The revision of the entire subversion repository that the numbers (stem counts, evaluation, etc.) in this paper represent is \texttt{r48137}.

%FIXME: update for the three languages
The tagset consists of 127 separate tags, 19 covering the main parts of speech (noun, verb, adjective, adverb, postposition, etc.) and 108 covering morphological subcategorisation for e.g. case, number, person, possession, transitivity, tense-aspect-mood, etc. The tags are represented as multicharacter symbols, between less than `<' and greater than `>' symbols. The tagset is quite extensive and still not entirely stabilised, as such a full listing is not included here. However, the tags are listed in the source code of the transducer,\footnote{no url needed?} along with comments describing their usage.
